Regular singular Volterra equations on complex domains

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Write bound on |f| instead of f

% revision highlighting
\newif\ifhighlightrevs
\highlightrevsfalse
\ifhighlightrevs
\newenvironment{rev}{\color{red!60!black}}{\color{black}}
\newcommand{\revtext}[1]{\textcolor{red!50!black}{#1}}
\else
\newenvironment{rev}{}{}
\newcommand{\revtext}[1]{#1}
\fi

% colors
\definecolor{ietocean}{RGB}{0, 30, 140}
\definecolor{ietcoast}{RGB}{0, 150, 173}
\definecolor{ietlagoon}{RGB}{0, 216, 180}
\definecolor{veriforest}{RGB}{0, 80, 40}

@@

Our results build on known methods for solving differential equations with irregular singularities. Our focus on integral equations in the position domain, and the singularities of their solutions, recalls the approach of Loday-Richaud and Remy, who use a mix of formal and analytic methods inspired by \'{E}calle's theory of resurgence~\cite{loday-Remy2011, EcalleIII}. One of our motivations is to understand resurgence from an analytic perspective, without reference to formal solutions. The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}. This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
\subsection{Formalism for coordinates}\label
\subsubsection{Rationale}
Our motivating example, equation~\eqref{eqn:intro-use-dict}, has regular singularities at various points $\zeta = \alpha$ on the position domain. Each associated solution $\psi_\alpha$ is most easily expressed in terms of its own translated position coordinate $\zeta_\alpha = \zeta - \alpha$. We therefore expect our results to be used in calculations involving multiple coordinates. Our formalism for points, functions, and coordinates is tailored to such calculations.

@@

The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}. \begin{rev}We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.
\begin{definition}\label{def:unif-exp}
For any $\Lambda \in \R$, let
\[ \singexp{0}{\Lambda}(\domain) \subset \holo(\domain) \]
be the subspace consisting of functions $f$ with $f \lesssim e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
\[ \|f\|_{0, \Lambda} := \sup_\Omega e^{-\Lambda|\zeta|}\,|f|. \]
\end{definition}
With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{rmk}
The subspace of functions of exponential type $\Lambda$ strictly contains $\singexp{0}{\Lambda}(\domain)$. A function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. Definition~\ref{def:unif-exp} instead requires a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.\end{rmk}
We now relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
\begin{definition}
For any $\sigma, \Lambda \in \R$, let
\[ \singexp{\sigma}{\Lambda}(\domain) \subset \holo(\domain) \]
be the subspace consisting of functions $f$ with $f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]
\end{definition}
The inclusion $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is again continuous.
\begin{proposition}\label{exp-complete}
The space $\singexp{\sigma}{\Lambda}(\domain)$ is complete.
\end{proposition}
\begin{proof}
Take a Cauchy sequence $(f_j)_{j \in \N}$ in $\singexp{\sigma}{\Lambda}(\domain)$. This sequence is Cauchy in $\holo(\domain)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is bounded with respect to each of the seminorms on $\holo(\domain)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \domain$. Since $\holo(\domain)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\domain)$ will always converge in the topology of $\holo(\domain)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.

>>>>

% revision highlighting
\newif\ifhighlightrevs
\highlightrevstrue
\ifhighlightrevs
\newenvironment{rev}{\color{revred}}{\color{black}}
\newcommand{\revtext}[1]{\textcolor{revred}{#1}}
\else
\newenvironment{rev}{}{}
\newcommand{\revtext}[1]{#1}
\fi

% colors
\definecolor{ietocean}{RGB}{0, 30, 140}
\definecolor{ietcoast}{RGB}{0, 150, 173}
\definecolor{ietlagoon}{RGB}{0, 216, 180}
\definecolor{veriforest}{RGB}{0, 80, 40}
\definecolor{revred}{RGB}{153, 0, 0}

@@

Our results build on known methods for solving differential equations with irregular singularities. Our focus on integral equations in the position domain, and the singularities of their solutions, recalls the approach of Loday-Richaud and Remy, who use a mix of formal and analytic methods inspired by \'{E}calle's theory of resurgence~\cite{loday-Remy2011, EcalleIII}. One of our motivations is to understand resurgence from an analytic perspective, without reference to formal solutions. The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}. This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
\subsection{Formalism for coordinates}\label{sec:formalism}
\subsubsection{Rationale}
Our motivating example, equation~\eqref{eqn:intro-use-dict}, has regular singularities at various points $\zeta = \alpha$ on the position domain. Each associated solution $\psi_\alpha$ is most easily expressed in terms of its own translated position coordinate $\zeta_\alpha = \zeta - \alpha$. We therefore expect our results to be used in calculations involving multiple coordinates. Our formalism for points, functions, and coordinates is tailored to such calculations.

@@

The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}. \begin{rev}We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.
\begin{definition}\label{def:unif-exp}
For any $\Lambda \in \R$, let
\[ \singexp{0}{\Lambda}(\domain) \subset \holo(\domain) \]
be the subspace consisting of functions $f$ with $|f| \lesssim e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
\[ \|f\|_{0, \Lambda} := \sup_\Omega e^{-\Lambda|\zeta|}\,|f|. \]
\end{definition}
With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$. That means the inclusion is continuous.
\begin{rmk}
The subspace of functions of exponential type $\Lambda$ strictly contains $\singexp{0}{\Lambda}(\domain)$. A function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. Definition~\ref{def:unif-exp} instead requires a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.\end{rmk}
We now relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
\begin{definition}
For any $\sigma, \Lambda \in \R$, let
\[ \singexp{\sigma}{\Lambda}(\domain) \subset \holo(\domain) \]
be the subspace consisting of functions $f$ with $|f| \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]
\end{definition}
The inclusion $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is again continuous.
\begin{proposition}\label{exp-complete}
The space $\singexp{\sigma}{\Lambda}(\domain)$ is complete.
\end{proposition}
\begin{proof}
Take a Cauchy sequence $(f_j)_{j \in \N}$ in $\singexp{\sigma}{\Lambda}(\domain)$. This sequence is Cauchy in $\holo(\domain)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is bounded with respect to each of the seminorms on $\holo(\domain)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \domain$. Since $\holo(\domain)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\domain)$ will always converge in the topology of $\holo(\domain)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.
